Model Adaptivity for Goal-Oriented Inference using Adjoints

### 2016-12-14 paper/paper_v4_cmame.tex
adding edits from karen
fixing latex formatting issues in cmame version

\begin{document}
\raggedbottom %avoid weird vertical justification

@@

\author{Harriet Li\textsuperscript{a,}\footnote{\red{Corresponding author ? \textit{Email address: foo@bar.edu}}}, Vikram Garg\textsuperscript{b}, Karen Willcox\textsuperscript{c}}
\address{\textsuperscript{a} Department of Aeronautics and Astronautics, Massachusetts Institute of Technology, Cambridge, MA, 02139, USA; \texttt{kameeko@mit.edu}\protect\\
\textsuperscript{b} Institute for Computational Engineering and Sciences, University of Texas, Austin, TX, 78712, USA; \texttt{vikram.v.garg@gmail.com}\protect\\
\textsuperscript{c} Department of Aeronautics and Astronautics, Massachusetts Institute of Technology, Cambridge, MA, 02139, USA; \texttt{kwillcox@mit.edu}}
%\date{}
\maketitle

\begin{abstract}
\input{abstract_v3.tex}
\end{abstract}

\begin{keyword}
  inference \sep goal-oriented adaptive modeling \sep a posteriori error estimation \sep multifidelity modeling \sep adjoints
\end{keyword}

\input{intro_v3_cmame.tex}
\input{mathematical_formulation_v3_cmame.tex}
\input{algorithms_v3_cmame.tex}
\input{numerical_experiments_v3_cmame.tex}
\input{conclusions_v3_cmame.tex}
\input{acknow.tex}

\section*{References}
\bibliographystyle{plain}
\bibliography{masterBib}
\end{document}

>>>>

\begin{document}
%\raggedbottom %avoid weird vertical justification

\begin{frontmatter}

@@

%\author{Harriet Li\textsuperscript{a,}\footnote{Corresponding author. \textit{Email address: kameeko@mit.edu}}, Vikram Garg\textsuperscript{b}, Karen Willcox\textsuperscript{c}}
%\address{\textsuperscript{a} Department of Aeronautics and Astronautics, Massachusetts Institute of Technology, Cambridge, MA, 02139, USA; \texttt{kameeko@mit.edu}\protect\\
%\textsuperscript{b} Institute for Computational Engineering and Sciences, University of Texas, Austin, TX, 78712, USA; \texttt{vikram.v.garg@gmail.com}\protect\\
%\textsuperscript{c} Department of Aeronautics and Astronautics, Massachusetts Institute of Technology, Cambridge, MA, 02139, USA; \texttt{kwillcox@mit.edu}}
%\date{}
%\maketitle

\author[adr1]{Harriet Li\corref{cor1}}
\cortext[cor1]{Corresponding author. \textit{Email address: kameeko@mit.edu}}
\address[adr1]{Department of Aeronautics and Astronautics, Massachusetts Institute of Technology, Cambridge, MA, 02139, USA; \texttt{kameeko@mit.edu}}
\author[adr2]{Vikram Garg}
\address[adr2]{Institute for Computational Engineering and Sciences, University of Texas, Austin, TX, 78712, USA; \texttt{vikram.v.garg@gmail.com}}
\author[adr3]{Karen Willcox}
\address[adr3]{Department of Aeronautics and Astronautics, Massachusetts Institute of Technology, Cambridge, MA, 02139, USA; \texttt{kwillcox@mit.edu}}

\begin{abstract}
\input{abstract_v4.tex}
\end{abstract}

\begin{keyword}
  inference \sep goal-oriented adaptive modeling \sep a posteriori error estimation \sep multi-fidelity modeling \sep adjoints
\end{keyword}

\end{frontmatter}

\input{intro_v4_cmame.tex}
\input{mathematical_formulation_v4_cmame.tex}
\input{algorithms_v4_cmame.tex}
\input{numerical_experiments_v4_cmame.tex}
\input{conclusions_v4_cmame.tex}
\input{acknow.tex}

\section*{References}
%\bibliographystyle{plain}
\bibliographystyle{elsarticle-harv} %this seems to get initials in bibliography, without doing name-year citation style as bst file claims?
\bibliography{masterBib}
\end{document}
